Galaxy Clustering Constraints on the Galaxy Size--Halo Connection

### 2017-08-31 paper/galsize_paper.tex
Finished formal description of the y-axis in upshot clustering figure

\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{hyperref}

@@

We calculate two-point clustering $\wproj$ with line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}. Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon composite galaxy size $\rhalf.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs. ``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalf\vert\mstar\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$

@@

\subsection{Baseline Mock Catalog}
\label{subsec:baselinemock}

@@

@@

>>>>

\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{color}

@@

We calculate two-point clustering $\wproj$ of our SDSS galaxy sample using line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}. Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon composite galaxy size $\rhalf.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs. ``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalf\vert\mstar\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$

@@

\subsection{Baseline Model and Mock Measurements}
\label{subsec:baselinemock}

@@

\subsection{Mock Measurements of Clustering and Lensing}
\label{subsec:mock_measurements}

For mock galaxies, to compute galaxy clustering we employ the distant observer approximation by treating the simulation $z-$axis as the line-of-sight. We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.

@@

In this section we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj.$ Galaxy clustering has complex, simultaneous dependence upon $\mstar,$ $\ssfr,$ $\rhalf,$ and $\bt.$ Since the purpose of this work is to test models of composite galaxy size $\rhalf,$ we design a measurement that is specifically tailored to isolate the influence of $\rhalf$ on the two-point function, while minimizing the dependence upon the other correlated variables.

To achieve this, we compute projected clustering separately for $\mstar-$complete samples of galaxies defined by simultaneous cuts on $\bt$ and $\rhalf,$ described as follows. First, we construct subsamples of disk-dominated and bulge-dominated galaxies using cuts of $\bt<0.25$ and $\bt>0.75,$ respectively, as in \S~\ref{subsubsec:scaling_relation} above. Separately for each $\bt-$selected subsample, we calculate $\rangle\rhalf\vert\mstar\rangle,$ the median composite size of the sample as a function of total galaxy stellar mass. We split each $\bt-$selected sample in half according to whether the galaxy has a composite size $\rhalf$ that is above or below this median value. For any $\mstar-$complete threshold, this gives four subsamples of large and small, disk- and bulge-dominated galaxies. For each $\bt-$selected sample, we calculate the difference $\wproj^{\rm large}-\wproj^{\rm small},$ scaled by $\wproj^{\rm all},$ the clustering of the $\bt-$selected sample prior to splitting on $\rhalf,$ and refer to this quantity as {\em the $\rhalf$ clustering ratio}.

The y-axis of each panel in Figure \ref{fig:clustering_ratio_upshot} shows these $\rhalf$ clustering ratios, with left and right panels showing measurements for $\mstar>10^{10}M_{\odot}$ and $\mstar>10^{10.5}M_{\odot}$ thresholds in total stellar mass, and top and bottom panels showing results for disk- and bulge-dominated samples, respectively.
